Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-07-29 ms.tex
I fixed some multiply defined labels.

The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time. A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:DHSvsNIRISS209}
\end{figure}

>>>>

The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST.
Figure \ref{fig:saturationLim} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms.
Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4.
The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS) \citep{ricker2014tess}.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time. A metallicity of 22 $\times$ solar from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
\end{figure}
